\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-02-07 analysis/paper/paper.Rmd
code clean up to fix conflits

```{r supportSetUp, echo = FALSE, eval = eval_cs3}
completeData=casebase::support
#remove hospital dead
completeData<-completeData[,-c(4)]
rat=1  #universal ratio for eval_cs3
#keep one individual out, at random, for which we will develop an 
#absolute risk curve.
#sam=sample(1:nrow(completeData), 1)
#Set workingData to the remaining individuals in the data
#workingData=completeData[-c(sam),]
workingCompleteData=model.matrix(death~ .-d.time,data=completeData)[,-c(1)]#remove intercept
#Create u and xCox, which will be used when fitting Cox with glmnet.
newData=workingCompleteData
x=workingCompleteData
#x and y will be used to fit the casebase model under glmnet.
#x=as.matrix(sparse.model.matrix(death~ .-d.time+0,data=workingData))
y=data.matrix(completeData[,c(2,5)])
```

>>>>

```{r supportSetUp, echo = FALSE, eval = eval_cs3}
completeData=casebase::support
#remove hospital dead
completeData<-completeData[,-c(4)]
ratio=10  #universal ratio for eval_cs3
#keep one individual out, at random, for which we will develop an 
#absolute risk curve.
#sam=sample(1:nrow(completeData), 1)
#Set workingData to the remaining individuals in the data
#workingData=completeData[-c(sam),]
workingCompleteData=model.matrix(death~ .-d.time,data=completeData)[,-c(1)]#remove intercept
#Create u and xCox, which will be used when fitting Cox with glmnet.
newData=workingCompleteData
x=workingCompleteData
#x and y will be used to fit the casebase model under glmnet.
#x=as.matrix(sparse.model.matrix(death~ .-d.time+0,data=workingData))
y=data.matrix(completeData[,c(2,5)])
```
